--- 
title: "MATA'EA, French Polynesia"
subtitle: "Arboviruses"
output:  
  html_document: 
    mode: selfcontained
    toc: yes 
    toc_float: true
    number_sections: false
    theme: flatly
fig_width: 12 
fig_caption: FALSE 
--- 
  
```{r setup, include=FALSE} 
# Chapter 1
# Set options, load data, utility functions 
knitr::opts_chunk$set(
  echo = FALSE,
  results = "asis",
  message = FALSE,
  warning = FALSE
)
library(data.table)
library(here)
library(haven)
library(knitr)
library(gtsummary)
library(flextable)
library(survey)
library(gt)
theme_gtsummary_language('en')
theme_gtsummary_journal('lancet')

load(here('data/rep.rdata'))

```


## 4.1 Dengue serotype 1 results

### Table 4.1.1 Dengue 1 seroprevalence

```{r tab_4_1_1}

d4 <- survey::svydesign(
  id = ~ subjid,
  weights = ~ w.arbo,
  strata = ~ geo + agegr,
  data = mata[!is.na(denv1), .(subjid,
                              w.arbo,
                              geo,
                              agegr,
                              sex,
                              bmi,
                              bm,
                              bm2,
                              overweight,
                              obese, 
                              denv1, 
                              denv2, 
                              denv3, 
                              denv4, 
                              zikv, 
                              chikv, 
                              rrv)]
)


tbl_svysummary(d4,
               include = c(denv1),
               missing='no',
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  modify_header(stat_0 = "**Dengue 1 (95% CI)**") |>
  bold_labels() |>  
  remove_row_type(type = 'level', level_value = 'Negative') |>
  remove_row_type(type='header')

```

### Table 4.1.2 Dengue 1 seroprevalence by sex

```{r tab_4_1_2}
tbl_svysummary(d4,
               include = c(denv1),
               missing = 'no',
               by = sex,
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "**Dengue 1**") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  bold_labels() |>
  remove_row_type(type = 'level', level_value = 'Negative') |>
  remove_row_type(type='header')

```


### Table 4.1.3 Dengue 1 seroprevalence by age

```{r tab_4_1_3}

tbl_svysummary(d4,
               include = c(denv1),
               missing = 'no',
               by = agegr,
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "**Dengue 1**") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  bold_labels() |>
  remove_row_type(type = 'level', level_value = 'Negative') |>
  remove_row_type(type='header')

```

### Table 4.1.4 Dengue 1 seroprevalence by archipelago

```{r tab_4_1_4}

tbl_svysummary(d4,
               include = c(denv1),
               missing = 'no',
               by = geo,
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "**Dengue 1**") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  bold_labels() |>
  remove_row_type(type = 'level', level_value = 'Negative') |>
  remove_row_type(type='header')

```






## 4.2 Dengue serotype 2 results

### Table 4.2.1 Dengue 2 seroprevalence

```{r tab_4_2_1}

tbl_svysummary(d4,
               include = c(denv2),
               missing='no',
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  modify_header(stat_0 = "**Dengue 2 (95% CI)**") |>
  bold_labels() |>  
  remove_row_type(type = 'level', level_value = 'Negative') |>
  remove_row_type(type='header')

```

### Table 4.2.2 Dengue 2 seroprevalence by sex

```{r tab_4_2_2}

tbl_svysummary(d4,
               include = c(denv2),
               missing = 'no',
               by = sex,
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "**Dengue 2**") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  bold_labels() |>
  remove_row_type(type = 'level', level_value = 'Negative') |>
  remove_row_type(type='header')

```


### Table 4.2.3 Dengue 2 seroprevalence by age

```{r tab_4_2_3}

tbl_svysummary(d4,
               include = c(denv2),
               missing = 'no',
               by = agegr,
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "**Dengue 2**") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  bold_labels() |>
  remove_row_type(type = 'level', level_value = 'Negative') |>
  remove_row_type(type='header')

```

### Table 4.2.4 Dengue 2 seroprevalence by archipelago

```{r tab_4_2_4}

tbl_svysummary(d4,
               include = c(denv2),
               missing = 'no',
               by = geo,
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "**Dengue 2**") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  bold_labels() |>
  remove_row_type(type = 'level', level_value = 'Negative') |>
  remove_row_type(type='header')

```






## 4.3 Dengue serotype 3 results

### Table 4.3.1 Dengue 3 seroprevalence

```{r tab_4_3_1}

tbl_svysummary(d4,
               include = c(denv3),
               missing='no',
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  modify_header(stat_0 = "**Dengue 3 (95% CI)**") |>
  bold_labels() |>  
  remove_row_type(type = 'level', level_value = 'Negative') |>
  remove_row_type(type='header')

```

### Table 4.3.2 Dengue 3 seroprevalence by sex

```{r tab_4_3_2}
tbl_svysummary(d4,
               include = c(denv3),
               missing = 'no',
               by = sex,
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "**Dengue 3**") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  bold_labels() |>
  remove_row_type(type = 'level', level_value = 'Negative') |>
  remove_row_type(type='header')

```


### Table 4.3.3 Dengue 3 seroprevalence by age

```{r tab_4_3_3}

tbl_svysummary(d4,
               include = c(denv3),
               missing = 'no',
               by = agegr,
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "**Dengue 3**") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  bold_labels() |>
  remove_row_type(type = 'level', level_value = 'Negative') |>
  remove_row_type(type='header')

```

### Table 4.3.4 Dengue 3 seroprevalence by archipelago

```{r tab_4_3_4}

tbl_svysummary(d4,
               include = c(denv3),
               missing = 'no',
               by = geo,
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "**Dengue 3**") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  bold_labels() |>
  remove_row_type(type = 'level', level_value = 'Negative') |>
  remove_row_type(type='header')

```






## 4.4 Dengue serotype 4 results

### Table 4.4.1 Dengue 4 seroprevalence

```{r tab_4_4_1}

tbl_svysummary(d4,
               include = c(denv4),
               missing='no',
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  modify_header(stat_0 = "**Dengue 4 (95% CI)**") |>
  bold_labels() |>  
  remove_row_type(type = 'level', level_value = 'Negative') |>
  remove_row_type(type='header')

```

### Table 4.4.2 Dengue 4 seroprevalence by sex

```{r tab_4_4_2}

tbl_svysummary(d4,
               include = c(denv4),
               missing = 'no',
               by = sex,
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "**Dengue 4**") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  bold_labels() |>
  remove_row_type(type = 'level', level_value = 'Negative') |>
  remove_row_type(type='header')

```


### Table 4.4.3 Dengue 4 seroprevalence by age

```{r tab_4_4_3}

tbl_svysummary(d4,
               include = c(denv4),
               missing = 'no',
               by = agegr,
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "**Dengue 4**") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  bold_labels() |>
  remove_row_type(type = 'level', level_value = 'Negative') |>
  remove_row_type(type='header')

```

### Table 4.4.4 Dengue 4 seroprevalence by archipelago

```{r tab_4_4_4}

tbl_svysummary(d4,
               include = c(denv4),
               missing = 'no',
               by = geo,
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "**Dengue 4**") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  bold_labels() |>
  remove_row_type(type = 'level', level_value = 'Negative') |>
  remove_row_type(type='header')

```






## 4.5 Zika results

### Table 4.5.1 Zika seroprevalence

```{r tab_4_5_1}

tbl_svysummary(d4,
               include = c(zikv),
               missing='no',
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  modify_header(stat_0 = "**Zika (95% CI)**") |>
  bold_labels() |>  
  remove_row_type(type = 'level', level_value = 'Negative') |>
  remove_row_type(type='header')

```

### Table 4.5.2 Zika seroprevalence by sex

```{r tab_4_5_2}
tbl_svysummary(d4,
               include = c(zikv),
               missing = 'no',
               by = sex,
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "**Zika**") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  bold_labels() |>
  remove_row_type(type = 'level', level_value = 'Negative') |>
  remove_row_type(type='header')

```


### Table 4.5.3 Zika seroprevalence by age

```{r tab_4_5_3}

tbl_svysummary(d4,
               include = c(zikv),
               missing = 'no',
               by = agegr,
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "**Zika**") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  bold_labels() |>
  remove_row_type(type = 'level', level_value = 'Negative') |>
  remove_row_type(type='header')

```

### Table 4.5.4 Zika seroprevalence by archipelago

```{r tab_4_5_4}

tbl_svysummary(d4,
               include = c(zikv),
               missing = 'no',
               by = geo,
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "**Zika**") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  bold_labels() |>
  remove_row_type(type = 'level', level_value = 'Negative') |>
  remove_row_type(type='header')

```






## 4.6 Chikungunya results

### Table 4.6.1 Chikungunya seroprevalence

```{r tab_4_6_1}

tbl_svysummary(d4,
               include = c(chikv),
               missing='no',
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  modify_header(stat_0 = "**Chikungunya (95% CI)**") |>
  bold_labels() |>  
  remove_row_type(type = 'level', level_value = 'Negative') |>
  remove_row_type(type='header')

```

### Table 4.6.2 Chikungunya seroprevalence by sex

```{r tab_4_6_2}
tbl_svysummary(d4,
               include = c(chikv),
               missing = 'no',
               by = sex,
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "**Chikungunya**") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  bold_labels() |>
  remove_row_type(type = 'level', level_value = 'Negative') |>
  remove_row_type(type='header')

```


### Table 4.6.3 Chikungunya seroprevalence by age

```{r tab_4_6_3}

tbl_svysummary(d4,
               include = c(chikv),
               missing = 'no',
               by = agegr,
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "**Chikungunya**") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  bold_labels() |>
  remove_row_type(type = 'level', level_value = 'Negative') |>
  remove_row_type(type='header')

```

### Table 4.6.4 Chikungunya seroprevalence by archipelago

```{r tab_4_6_4}

tbl_svysummary(d4,
               include = c(chikv),
               missing = 'no',
               by = geo,
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "**Chikungunya**") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  bold_labels() |>
  remove_row_type(type = 'level', level_value = 'Negative') |>
  remove_row_type(type='header')

```





## 4.7 Ross River results

### Table 4.7.1 Ross River seroprevalence

```{r tab_4_7_1}

tbl_svysummary(d4,
               include = c(rrv),
               missing='no',
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  modify_header(stat_0 = "**Ross River (95% CI)**") |>
  bold_labels() |>  
  remove_row_type(type = 'level', level_value = 'Negative') |>
  remove_row_type(type='header')

```

### Table 4.7.2 Ross River seroprevalence by sex

```{r tab_4_7_2}
tbl_svysummary(d4,
               include = c(rrv),
               missing = 'no',
               by = sex,
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "**Ross River**") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  bold_labels() |>
  remove_row_type(type = 'level', level_value = 'Negative') |>
  remove_row_type(type='header')

```


### Table 4.7.3 Ross River seroprevalence by age

```{r tab_4_7_3}

tbl_svysummary(d4,
               include = c(rrv),
               missing = 'no',
               by = agegr,
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "**Ross River**") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  bold_labels() |>
  remove_row_type(type = 'level', level_value = 'Negative') |>
  remove_row_type(type='header')

```


### Table 4.7.4 Ross River seroprevalence by archipelago

```{r tab_4_7_4}

tbl_svysummary(d4,
               include = c(rrv),
               missing = 'no',
               by = geo,
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "**Ross River**") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  bold_labels() |>
  remove_row_type(type = 'level', level_value = 'Negative') |>
  remove_row_type(type='header')

```



## 4.8 Zika vs Dengue

### Table 4.8.1 Zika prevalence vs dengue 1, archipelago, age and sex, quasi-binomial regressions (bivariate and multivariate) ajusted for sampling design effects

```{r tab_4_8_1}

mata[, zika := as.numeric(factor(zikv)) - 1]

d4b <- survey::svydesign(
  id = ~ subjid,
  weights = ~ w.arbo,
  strata = ~ geo + agegr,
  data = mata[!is.na(denv1), .(subjid,
                              w.arbo,
                              geo,
                              agegr,
                              sex,
                              bmi,
                              bm,
                              bm2,
                              overweight,
                              obese, 
                              denv1, 
                              denv2, 
                              denv3, 
                              denv4, 
                              zikv,
                              zika,
                              chikv, 
                              rrv)]
)

t1 <- tbl_uvregression(d4b,
    method = svyglm,
    label = list(geo ~ "Archipelago", sex ~ "Sex", agegr ~ "Age group"),
    include = c('geo', 'sex', 'agegr', 'denv1','denv2','denv3','denv4'),
    hide_n = TRUE,
    y = zika,
    method.args = list(family = quasibinomial),
    exponentiate = TRUE
  ) |>
  modify_header(update = list(estimate ~ "**OR (IC 95%)**")) |>
#  add_q() |>
  modify_footnote(estimate = "OR = rapport de cotes, IC = intervalle de confiance", abbreviation = TRUE) |>
  add_significance_stars(hide_se = TRUE,
                         hide_p = FALSE,
                         pattern = "{p.value}{stars}")

m <-
  svyglm(
    zika ~ geo + sex + agegr + denv1 + denv2 + denv3 + denv4,
    design = d4b,
    family = "quasibinomial"
  )

t2 <- tbl_regression(m,
               label = list(geo ~ "Archipelago", sex ~ "Sex", agegr ~ "Age group"),
               exponentiate = TRUE) |>
  modify_header(update = list(estimate ~ "**aOR (IC 95%)**")) |>
  modify_footnote(estimate = "aOR = Adjusted odds ratio", abbreviation = TRUE) |>
#  add_global_p() |>
  add_significance_stars(
    hide_se = TRUE,
    hide_p = FALSE,
    pattern = "{p.value}{stars}"
  )
# modify_footnote(everything() ~ NA, abbreviation = TRUE)

tbl_merge(
  tbls        = list(t1, t2),
  tab_spanner = c("**Univariate analysis**", "**Multivariate analysis**"))

```


