--- 
title: "MATA'EA, French Polynesia"
subtitle: "Lipid profiles"
output:  
  html_document: 
    mode: selfcontained
    toc: yes 
    toc_float: true
    number_sections: false
    theme: flatly
fig_width: 12 
fig_caption: FALSE 
--- 
  
```{r setup, include=FALSE} 
# Chapter 1
# Set options, load data, utility functions 
knitr::opts_chunk$set(
  echo = FALSE,
  results = "asis",
  message = FALSE,
  warning = FALSE
)
library(data.table)
library(here)
library(haven)
library(knitr)
library(gtsummary)
library(flextable)
library(survey)
library(gt)
theme_gtsummary_language('en')
theme_gtsummary_journal('lancet')

load(here('data/rep.rdata'))

```


## 2.1 Cholesterol results

### Table 2.1.1 Cholesterol categories

```{r tab_2_1_1}

d2 <- survey::svydesign(
  id = ~ subjid,
  weights = ~ w.lipid,
  strata = ~ geo + agegr,
  data = mata[!is.na(chol), .(subjid,
                              w.lipid,
                              geo,
                              agegr,
                              sex,
                              bmi,
                              bm,
                              bm2,
                              overweight,
                              obese,
                              tg,
                              chol,
                              hdl,
                              hdl.ratio,
                              ldl,
                              hdlldl.ratio)]
)


tbl_svysummary(d2,
               include = c(chol),
               missing='no',
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  modify_header(stat_0 = "**Cholesterol (95% CI)**") |>
  bold_labels() |>
  remove_row_type(type='header')

```

### Table 2.1.2 Cholesterol by sex

```{r tab_2_1_2}
tbl_svysummary(d2,
               include = c(chol),
               missing = 'no',
               by = sex,
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "**Cholesterol**") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  bold_labels() |>
  remove_row_type(type='header')

```


### Table 2.1.3 Cholesterol by age

```{r tab_2_1_3}

tbl_svysummary(d2,
               include = c(chol),
               missing = 'no',
               by = agegr,
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "**Cholesterol**") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  bold_labels() |>
  remove_row_type(type='header')

```

### Table 2.1.4 Cholesterol by archipelago

```{r tab_2_1_4}

tbl_svysummary(d2,
               include = c(chol),
               missing = 'no',
               by = geo,
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "**Cholesterol**") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  bold_labels() |>
  remove_row_type(type='header')

```


### Table 2.1.5 Cholesterol by body mass categories

```{r tab_2_1_5}

tbl_svysummary(d2,
               include = c(chol),
               missing = 'no',
               by = bm2,
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "**Cholesterol**") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  bold_labels() |>
  remove_row_type(type='header')

```

## 2.2 Triglycerids results

### Table 2.2.1 Triglycerids categories

```{r tab_2_2_1}

tbl_svysummary(d2,
               include = c(tg),
               missing='no',
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  modify_header(stat_0 = "**Blood cholesterol (95% CI)**") |>
  bold_labels() |>
  remove_row_type(type='header')

```

### Table 2.2.2 Triglycerids by sex

```{r tab_2_2_2}

tbl_svysummary(d2,
               include = c(tg),
               missing = 'no',
               by = sex,
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "**Triglycerids**") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  bold_labels() |>
  remove_row_type(type='header')

```


### Table 2.2.3 Triglycerids by age

```{r tab_2_2_3}

tbl_svysummary(d2,
               include = c(tg),
               missing = 'no',
               by = agegr,
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "**Triglycerids**") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  bold_labels() |>
  remove_row_type(type='header')

```

### Table 2.2.4 Triglycerids by archipelago

```{r tab_2_2_4}

tbl_svysummary(d2,
               include = c(tg),
               missing = 'no',
               by = geo,
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "**Triglycerids**") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  bold_labels() |>
  remove_row_type(type='header')

```

### Table 2.2.5 Triglycerids by body mass categories

```{r tab_2_2_5}

tbl_svysummary(d2,
               include = c(tg),
               missing = 'no',
               by = bm2,
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "**Triglycerids**") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  bold_labels() |>
  remove_row_type(type='header')

```


## 2.3 Cholesterol HDL results

### Table 2.3.1 Cholesterol HDL categories

```{r tab_2_3_1}

tbl_svysummary(d2,
               include = c(hdl),
               missing='no',
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  modify_header(stat_0 = "**Cholesterol HDL (95% CI)**") |>
  bold_labels() |>
  remove_row_type(type='header')

```

### Table 2.3.2 Cholesterol HDL by sex

```{r tab_2_3_2}
tbl_svysummary(d2,
               include = c(hdl),
               missing = 'no',
               by = sex,
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "**Cholesterol HDL**") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  bold_labels() |>
  remove_row_type(type='header')

```


### Table 2.3.3 Cholesterol HDL by age

```{r tab_2_3_3}

tbl_svysummary(d2,
               include = c(hdl),
               missing = 'no',
               by = agegr,
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "**Cholesterol HDL**") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  bold_labels() |>
  remove_row_type(type='header')

```

### Table 2.3.4 Cholesterol HDL by archipelago

```{r tab_2_3_4}

tbl_svysummary(d2,
               include = c(hdl),
               missing = 'no',
               by = geo,
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "**Cholesterol HDL**") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  bold_labels() |>
  remove_row_type(type='header')

```


### Table 2.3.5 Cholesterol HDL by body mass categories

```{r tab_2_3_5}

tbl_svysummary(d2,
               include = c(hdl),
               missing = 'no',
               by = bm2,
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "**Cholesterol HDL**") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  bold_labels() |>
  remove_row_type(type='header')

```


## 2.4 Ratio total cholesterol / HDL

### Table 2.4.1 Cholesterol/HDL ratio categories

```{r tab_2_4_1}

tbl_svysummary(d2,
               include = c(hdl.ratio),
               missing='no',
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  modify_header(stat_0 = "**Cholesterol/HDL (95% CI)**") |>
  bold_labels() |>
  remove_row_type(type='header')

```

### Table 2.4.2 Cholesterol/HDL ratio by sex

```{r tab_2_4_2}
tbl_svysummary(d2,
               include = c(hdl.ratio),
               missing = 'no',
               by = sex,
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "**Cholesterol/HDL**") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  bold_labels() |>
  remove_row_type(type='header')

```


### Table 2.4.3 Cholesterol/HDL ratio by age

```{r tab_2_4_3}

tbl_svysummary(d2,
               include = c(hdl.ratio),
               missing = 'no',
               by = agegr,
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "**Cholesterol/HDL**") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  bold_labels() |>
  remove_row_type(type='header')

```

### Table 2.4.4 Cholesterol/HDL ratio by archipelago

```{r tab_2_4_4}

tbl_svysummary(d2,
               include = c(hdl.ratio),
               missing = 'no',
               by = geo,
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "**Cholesterol/HDL**") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  bold_labels() |>
  remove_row_type(type='header')

```


### Table 2.4.5 Cholesterol/HDL ratio by body mass categories

```{r tab_2_4_5}

tbl_svysummary(d2,
               include = c(hdl.ratio),
               missing = 'no',
               by = bm2,
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "**Cholesterol/HDL**") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  bold_labels() |>
  remove_row_type(type='header')

```







## 2.5 Cholesterol LDL results

### Table 2.5.1 Cholesterol LDL categories

```{r tab_2_5_1}

tbl_svysummary(d2,
               include = c(ldl),
               missing='no',
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  modify_header(stat_0 = "**Cholesterol LDL (95% CI)**") |>
  bold_labels() |>
  remove_row_type(type='header')

```

### Table 2.5.2 Cholesterol LDL by sex

```{r tab_2_5_2}
tbl_svysummary(d2,
               include = c(ldl),
               missing = 'no',
               by = sex,
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "**Cholesterol LDL**") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  bold_labels() |>
  remove_row_type(type='header')

```


### Table 2.5.3 Cholesterol LDL by age

```{r tab_2_5_3}

tbl_svysummary(d2,
               include = c(ldl),
               missing = 'no',
               by = agegr,
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "**Cholesterol LDL**") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  bold_labels() |>
  remove_row_type(type='header')

```

### Table 2.5.4 Cholesterol LDL by archipelago

```{r tab_2_5_4}

tbl_svysummary(d2,
               include = c(ldl),
               missing = 'no',
               by = geo,
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "**Cholesterol LDL**") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  bold_labels() |>
  remove_row_type(type='header')

```


### Table 2.5.5 Cholesterol LDL by body mass categories

```{r tab_2_5_5}

tbl_svysummary(d2,
               include = c(ldl),
               missing = 'no',
               by = bm2,
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "**Cholesterol LDL**") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  bold_labels() |>
  remove_row_type(type='header')

```


## 2.6 HDL/LDL cholesterol ratio

### Table 2.6.1 HDL/LDL cholesterol ratio categories

```{r tab_2_6_1}

tbl_svysummary(d2,
               include = c(hdlldl.ratio),
               missing='no',
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  modify_header(stat_0 = "**HDL/LDL (95% CI)**") |>
  bold_labels() |>
  remove_row_type(type='header')

```

### Table 2.6.2 HDL/LDL cholesterol ratio by sex

```{r tab_2_6_2}
tbl_svysummary(d2,
               include = c(hdlldl.ratio),
               missing = 'no',
               by = sex,
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "**HDL/LDL**") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  bold_labels() |>
  remove_row_type(type='header')

```


### Table 2.6.3 HDL/LDL cholesterol ratio by age

```{r tab_2_6_3}

tbl_svysummary(d2,
               include = c(hdlldl.ratio),
               missing = 'no',
               by = agegr,
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "**HDL/LDL**") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  bold_labels() |>
  remove_row_type(type='header')

```

### Table 2.6.4 HDL/LDL cholesterol ratio by archipelago

```{r tab_2_6_4}

tbl_svysummary(d2,
               include = c(hdlldl.ratio),
               missing = 'no',
               by = geo,
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "**HDL/LDL**") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  bold_labels() |>
  remove_row_type(type='header')

```


### Table 2.6.5 HDL/LDL cholesterol ratio by body mass categories

```{r tab_2_6_5}

tbl_svysummary(d2,
               include = c(hdlldl.ratio),
               missing = 'no',
               by = bm2,
               statistic = list(all_categorical() ~ "{p}")) |>
  modify_header(label ~ "**HDL/LDL**") |>
  add_ci(
    pattern = "{stat} ({ci})",
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}")
  )  |>
  bold_labels() |>
  remove_row_type(type='header')

```

